Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-07-13 doc/main_jfm.tex
fixed a renewcommand
worked on section 2

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\GG}{\mathbf{G}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\uu}{\mathbf{u}}
\newcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}

@@

\section{Governing  Equations}
\subsection{\label{mobility}Mobility Problem}
The governing equations of $N_b$-body particles suspended in the
two-dimensional, unbounded
domain $\Omega$ are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= 0 \qquad \qquad && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $\mu$ is viscosity, $p$ is the pressure, and $\uu_\infty$ is
the background flow. Each particle $\Gamma_i$ with center $\aa_i$ is
a rigid body, and its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity.
Here, $\langle x, y \rangle^{\perp} = \langle -y, x \rangle$.
Therefore, the no-slip boundary condition of
the velocity field is 
\begin{align}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \bd\Gamma_i.
\end{align}
To determine the translational and angular velocities of each rigid body,
we assume some imposed forces $\FF_i$ and torques $T_i$ acting on each particle.
Since the small particles are intertialess, force balance gives 
\begin{alignat}{2}
  \label{eqn:force}
  \FF_i &+ \int_{\bd\Gamma_i} \ssigma \cdot \nnu_i \, ds && = \mathbf{0}, \\
  \label{eqn:torque}
  T_i &+ \int_{\bd\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu_i) \, ds && = 0,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor).

\subsection{Imposed Forces}
The imposed forces and torques contain two parts. 
The first part comes from the hydrophobic attraction potential (HAP).
This potential was introduced in \cite{Fu20} and
models hydrophobic attraction by solving the screened Laplace equation boundary value problem
\begin{alignat}{2}
  \label{SL}
-\rho^2 \Delta u + u &=0,            && \mathbf{x} \in \Omega,\\
\label{SLbc}
u(\mathbf{x}) &= f_i(\mathbf{x}),\qquad  && \mathbf{x} \in \Gamma_i, \\
\label{SLff}
u &\to 0,                          &&|\mathbf{x}| \to \infty,
\end{alignat}
where $f_i$ is material label with $f_i = 0$, resp. $1$ representing hydrophilic, resp. hydrophobic, 
portions of the surface, and $\rho$ is the decay length of attraction.
The forces and torques for this attraction are 
\begin{align}
  \label{eqn:hydrophobicAttraction}
  \FF_i^{\text{hydro}} = \int_{\bd \Gamma_i} {\bf T}\cdot \nnu_i \, dS, 
    \quad 
  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu_i) dS,
\end{align}
where
\begin{equation}
  \label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
  u|^2 \mathbf{I} - \nabla u\otimes \nabla u\right)
\end{equation}
is the hydrophobic stress tensor.  The parameter $\gamma$ is interfacial tension. 
The forces $\FF_i^{\text{hydro}}$ and torques $T_i^{\text{hydro}}$ are responsible for
forming particle aggregates that partially sequester 
the hydrophobic portions of the particle surface.

The second part of the imposed forces and torques comes from repulsion between proximal particles.
We define 
\begin{equation}
  \label{REPUL}
  \FF_i^{\text{repul}} = \sum_{i=1}^{N_b} \frac{\mathbf{x}_{ij} - \mathbf{y}_{ij}}{\rho_{ij}} P(\rho_{ij}),\quad 
  T_i^{\text{repul}} = \sum_{i=1}^{N_b} (\mathbf{x}_{ij} - \mathbf{a}_i)^{\perp}\cdot \frac{\mathbf{x}_{ij} - \mathbf{y}_{ij}}{\rho_{ij}} P(\rho_{ij})
\end{equation}
where $\mathbf{x}_{ij} \in \partial \Gamma_i$, 
$\mathbf{y}_{ij} \in \partial \Gamma_j$, 
and $\rho_{ij} = |\mathbf{x}_{ij} - \mathbf{y}_{ij}|$
is the distance between the pair of particles.
The repulsion profile $P(r)$ is zero for distances $r$ larger than a repulsion length scale
$\rho_0$.  As such, \eqref{REPUL} ignores particles $\Gamma_j$ outside a tubular neighborhood
of $\Gamma_i$.  For $0 \leq r < \rho_0,$ we use $P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is sufficiently
large to prevent particle collisions.  The total imposed force and torque are
\begin{equation}
  \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
    T_i =   T_i^{\text{hydro}} +   T_i^{\text{repul}}.
\end{equation}

\subsection{Time marchning and Nondimensionalizations}
From the mobility problem, we obtain translational and angular velocities of the $N_b$-body system.
A second order Adam-Bashforth scheme updates the particle positions and orientations.
dynamics but body collisions may occur during the simulation while a relatively large time step is chosen.
We therefore impose a short range repulsion that it will be turned on when the distance between two boundary points on different bodies are within one characteristic length.

>>>>

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\GG}{\mathbf{G}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}

@@

\section{Governing  Equations}
\subsection{\label{mobility}Mobility Problem}
We consider a suspension of $N_b$ particles suspended in a
two-dimensional unbounded domain. The boundary of each particle is
denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1 \cup \Gamma_2 \cup
\cdots \cup \Gamma_{N_b}$. Assuming the flow is Stokesian, the governing
equations are
\begin{alignat}{3}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, \qquad \qquad 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $\mu$ is viscosity, $p$ is the pressure,
and $\uu_\infty$ is the background flow. Since each particle $\Gamma_i$
with center $\aa_i$ is a rigid body, its velocity satisfies 
\begin{align}
  \vv(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity.  Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$. Therefore, the no-slip boundary condition on each particle is
\begin{align}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
    \xx \in \Gamma_i.
\end{align}
To determine the translational and angular velocities of each particle,
we assume some imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are intertialess, force balance
gives 
\begin{alignat}{2}
  \label{eqn:force}
  \FF_i &+ \int_{\Gamma_i} \ssigma \cdot \nnu_i \, ds = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eqn:torque}
  T_i &+ \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu_i) \, ds = 0 \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor).

\subsection{Imposed Forces}
The imposed forces and torques contain two parts. 
The first part comes from the hydrophobic attraction potential (HAP).
This potential was introduced in \cite{Fu20} and
models hydrophobic attraction by solving the screened Laplace equation boundary value problem
\begin{alignat}{2}
  \label{SL}
-\rho^2 \Delta u + u &=0,            && \xx \in \Omega,\\
\label{SLbc}
u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i, \\
\label{SLff}
u &\to 0,                          &&|\xx| \to \infty,
\end{alignat}
where $f_i$ is material label with $f_i = 0$ ($1$) representing
hydrophilic (hydrophobic) portions of the surface, and $\rho$ is the
decay length of attraction.  The forces and torques for this attraction
are 
\begin{align}
  \label{eqn:hydrophobicAttraction}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu_i \, dS, 
    \quad 
  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu_i) dS,
\end{align}
where
\begin{align}
  \label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
  u|^2 \mathbf{I} - \nabla u\otimes \nabla u\right)
\end{align}
is the hydrophobic stress tensor. The parameter $\gamma$ is interfacial
tension. The forces $\FF_i^{\text{hydro}}$ and torques
$T_i^{\text{hydro}}$ are responsible for forming particle aggregates
that partially sequester the hydrophobic portions of the particle
surface.

The second part of the imposed forces and torques comes from repulsion
between proximal particles. We define 
\begin{align}
%  \label{eqn:REPUL}
%  \FF_i^{\text{repul}} = \sum_{i=1}^{N_b} \frac{\xx_{ij} -
%  \yy_{ij}}{\rho_{ij}} P(\rho_{ij}),\quad 
%  T_i^{\text{repul}} = \sum_{i=1}^{N_b} (\xx_{ij} - \aa_i)^{\perp}\cdot
%  \frac{\xx_{ij} - \yy_{ij}}{\rho_{ij}} P(\rho_{ij})
%
  \label{eqn:REPULforce}
  \FF_i^{\text{repul}} &= \sum_{j \neq i} \int_{\Gamma_j}
    \frac{\xx - \yy}{|\xx - \yy|} P(|\xx - \yy|)\, dS, \\
  \label{eqn:REPULtorque}
  T_i^{\text{repul}} &= \sum_{j \neq i} \int_{\Gamma_j}
    (\xx - \aa_i)^{\perp} \cdot 
    \frac{\xx - \yy}{|\xx - \yy|} P(|\xx - \yy|)\, dS, 
\end{align}
where $\xx \in \Gamma_i$ and $|\xx - \yy|$ is the distance between the
pair of particles. The repulsion profile $P(r)$ is zero for distances
$r$ larger than a repulsion length scale $\rho_0$. As
such,~\eqref{eqn:REPULforce} and~\eqref{eqn:REPULtorque} ignore
particles $\Gamma_j$ outside a tubular neighborhood of $\Gamma_i$. For
$0 \leq r < \rho_0,$ we use $P(r) = M(1 - \sin(r/\rho_0))$ where $M$ is
sufficiently large to prevent particle collisions. The total imposed
force and torque are
\begin{align}
  \FF_i = \FF_i^{\text{hydro}} + \FF_i^{\text{repul}},\quad
  T_i = T_i^{\text{hydro}} + T_i^{\text{repul}}, \qquad
  i=1,\ldots,N_b.
\end{align}

\subsection{Time Marching and Nondimensionalizations}
From the mobility problem, we obtain translational and angular velocities of the $N_b$-body system.
A second order Adam-Bashforth scheme updates the particle positions and orientations.
dynamics but body collisions may occur during the simulation while a relatively large time step is chosen.
We therefore impose a short range repulsion that it will be turned on when the distance between two boundary points on different bodies are within one characteristic length.
